### 2015-10-18 Assignment I/Assignment1-Ditz_Schroeder-WS15-16.tex
tzext text text

  \section*{Exercise 1 - \textsl{Smith Waterman today}}
	  The 30 years old Smith-Waterman (SW) algorithm is one of the fundamental algorithms in bioinformatics. This algorithm allows in a biological sense for example the detection of Domains in a protein or a Protein in a larger sequence. But the dynamic programmed algorithm has to face the problem of complexity of $O(n\times m)$. This complexity is getting a problem when starting to compare large sequences or even whole genomes.
	  The classical example for todays usage of the Smith Waterman algorithm is the BLAST algorithm. \cite{blast}

@@

\begin{thebibliography}{widestlabel}
	\bibitem[Li, H., Homer, N.]{blast} 	
	Li, H., Homer, N. (2010). A survey of sequence alignment algorithms for next-generation sequencing. Briefings in Bioinformatics, 11(5), 473–483. http://doi.org/10.1093/bib/bbq015
\end{thebibliography}

>>>>

  \section*{Exercise 1 - \textsl{Smith Waterman today}}
	  The 30 years old Smith-Waterman (SW) algorithm is one of the fundamental algorithms in bioinformatics. This dynamic programming (DP) algorithm allows in a biological sense for example the detection of Domains in a protein or a Protein in a larger sequence. But the algorithm has to face the problem of complexity of $O(n\times m)$. This complexity is getting a problem when starting to compare large sequences or even whole genomes. Still today has this algorithm a high importance in bioinformatics, which can be seen in the following examples.
	  The classical example for todays usage of the Smith Waterman algorithm is the BLAST algorithm. Which uses algorithm for seed refinement. Thereby the algorithm is accelerated with vectorization process. Basically this is an improvment on the hardwarelevel of a computer, which can be adressed by the software for parallelizing the alignment. As a result, the Smith-Waterman algorithm is accelerated by a factor of 10 in comparison to the standard algorithm Novoalign (http://novocraft.com). Also an advantage in complexity mattes is constraining the algorithm around seeds from the seeding step.
	   \cite{blast}
	  Parallelizing is general a very modern topic for Smith-Waterman Algorithms. Some research groups try to accelerate the algorithm by paralelizing the algorithm via a heterogeneous platform. On this platform they use the graphics processing unit and the central processing unit for an enhanced speed of the algorithm.
	  \cite{parallel}

@@

\begin{thebibliography}{widestlabel}
	\bibitem[Li, H., Homer, N.]{blast} 	
	Li, H., Homer, N. (2010). A survey of sequence alignment algorithms for next-generation sequencing. Briefings in Bioinformatics, 11(5), 473–483. http://doi.org/10.1093/bib/bbq015
	\bibitem[Chen, B. and Xu, Y. et al]{parallel} 		
		Chen, B. and Xu, Y. and Yang, J. and Jiang, H. (2010). A New Parallel Method of Smith-Waterman Algorithm on a Heterogeneous Platform. Springer. Algorithms and Architectures for Parallel Processing.79–90
\end{thebibliography}
